---
title: "Homework 6"
author: "Jyoti Ankam"
date: "November 25, 2018"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(message = FALSE)
```

Installing the required libraries

```{r}
library(tidyverse)
library(modelr)
```

Problem 1
Reading in the dataset using read_csv. We will now create a city_with_state variable (e.g. “Baltimore, MD”), and a binary variable showing if the homicide was solved. Additionally, we will also remove the follwing states - Phoenix, AZ; Dallas, TX; and Kansas City, MO as these states do not report the victim's races and also Tulsa, AL as this seems to be an error in data entry.

Next we will modify victim_race such that it has the categories white and non-white, making white the reference category and making victim_age numeric.

```{r}
hom_df = read_csv("https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv", col_names = TRUE) %>% 
  mutate(city_with_state = str_c(city, ",", " ", state),
         solved = if_else(disposition == "Closed by arrest", "resolved", "unresolved"),
         solved = fct_relevel(solved, "unresolved"),
         victim_race = tolower(victim_race),
         colpsd_victim_race = fct_collapse(victim_race, "non-white" = c("asian","black", "hispanic", "other", "unknown")),
         colpsd_victim_race = fct_relevel(colpsd_victim_race, "white"),
         victim_age = as.numeric(victim_age)) %>% 
  filter(!(city_with_state %in% c("Phoenix, AZ", "Dallas, TX", "Kansas City, MO", "Tulsa, AL")))

```

